Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-12-16 paper/main.tex
minor

\begin{figure}[h]
    \begin{tabular}{|r|r|r|r|r|}
        \hline
                       &\eval & \texttt{evalq} & \texttt{eval.parent} & \texttt{local} \\
       Static    sites  & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
       Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
        Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\
%        \% triggered & \Triggeredevalpercent & \Triggeredevalqpercent & \Triggeredevalparentpercent & \Triggeredlocalpercent \\
        \hline
    \end{tabular}
    \caption{Variants of \eval} \label{tab:variantseval}
\end{figure}

@@

(\EvalsRnd for \eval, \EvalqsRnd for \c{evalq}, \EparentsRnd for
\c{eval.parent} and \LocalsRnd for \c{local}).

\NbPackageEvalAtLeastOnce packages in our corpus call \eval at least once.

\mypara{Number of eval call sites.}  We observed that the number of
\eval call sites is small.  Figure~\ref{fig:callSitesPerPackage} shows
a violin plot of the distribution of call sites to \eval and its three
variants. For packages that have call sites, the median is
\NbMedianCallSites call sites. \NbOneCallSite{} packages have a single
call site, and one package, \emph{\MaxCallSitesPackage}, has
\MaxCallSites{} call sites. \PackagesNoCallsToEval{} packages have no
calls sites to \eval. These numbers are under-approximations as \eval
may be aliased, called reflectively and given as argument to a
higher-order function such as \c{map}.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{call_sites_per_packages}
	\caption{Violin plot of the call sites per packages per eval function. } \label{fig:callSitesPerPackage}
\end{figure}

>>>>

\begin{figure}[h]\begin{tabular}{|r|r|r|r|r|}\hline
   &\eval & \c{evalq} & \c{eval} & \c{local} \\[-2mm]
           & & & \c{.parent} & \\\hline
Static sites  & \Staticeval & \Staticevalq & \Staticevalparent & \Staticlocal \\
Exercised sites & \Triggeredeval & \Triggeredevalq & \Triggeredevalparent & \Triggeredlocal \\
Invocations & \EvalsRnd & \EvalqsRnd & \EparentsRnd & \LocalsRnd \\\hline
\end{tabular}\caption{Variants}\label{tab:variantseval}
\end{figure}

Figure~\ref{tab:variantseval} shows, per variant of \eval, the number
of call sites in the corpus (\emph{static}), the number of call sites
that were observed during tracing (\emph{exercised}), and the total
number of dynamic calls (\emph{invocations}). The data clearly shows
that the variants of \eval are rarely used, in particular \c{evalq}
and \c{local}.

@@
